Analytical Model for the Current Density in the Electrochemical Synthesis of Porous Silicon Structures with a Lateral Gradient

### 2021-01-22 paper.tex
Rename figures to fig1, fig2, etc.
Rename bibliography file
Correct couple of spelling mistakes

We assume that our electrolytic cell has the shape of a rectangular
prism (see Fig. \ref{f:celda}) with a horizontal base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is an
electrically grounded relatively good conductor. Within the electrolyte we position an electrode
which we assume is a thin conducting wire, insulated from the electrolyte
but for a small tip, which we approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{celdan1.png}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid. The current flows through the electrolyte from the sample
    to the tip.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. In a
stationary situation
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, the potential
obeys Laplace's equation within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through, and the sign is consistent with the current direction in
Fig. \ref{f:celda}. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

  \includegraphics[width=\textwidth]{paper-1}

@@

  \includegraphics[width=\textwidth]{paper-2}

@@

The current density normal to the surface may now be obtained as
$j_\perp=-\sigma\partial\phi/\partial z$,
\begin{equation}
  \label{Eq:J}
  \begin{split}
    j_\perp(\bm r) =& \frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
      Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
    &\times \cosh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
  \end{split}
\end{equation}
Eq. \eqref{Eq:J} is a very rapidly convergent expression that allows,
in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
the substrate to produce the PS sample. As expected, the current
at the surface $z=0$ of the sample becomes more homogeneous as the
distance $z_0$ to the tip of the electrode and the height of the
electrolite $c>z_0$ increase, as each term in the sum decays
approximately exponentially with increasing $z_0$.
Integrating over the surface of the sample we verify
\begin{equation}
  \label{eq:intj}
  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=I,
\end{equation}
as the contributions of opposite non-null reciprocal vectors cancel
out: as expected, all the charges that leave the sample find
their way  to the cathode across the electrolyte.

@@

\section{Procedures}
\label{sec:procedures}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-5}

@@

\section{Results and Discussion}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \begin{picture}(400,300)
    \put(0,0){\includegraphics[width=.8\textwidth]{j_Ivsx.png}}
    \put(160,140){\includegraphics[trim=50 50 70 80,clip,width=.4\textwidth]{j_Ivsxy.png}}
  \end{picture}
  \caption{Normalized current density $j_\perp(x,y,0)/I$ for a system
    as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
    the surface of the electrolyte at a height $c=1.0\,\text{cm}$, with a
    point-like electrode at $\bm r_0=(0.2\,\text{cm},
    0.74\,\text{cm},0.9\,\text{cm})$,  calculated through
    Eq. (\ref{Eq:J}) along the center line
    $y=0.74\,\text{cm}$. Inset: current over the whole surface.}
  \label{fig:DR1}
\end{figure}
In Fig. \ref{fig:DR1} we show the normalized current density $j_\perp(x,y,0)/I$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
that vary mostly along the $x$ direction. Of course, this would differ
for cells with different aspect ratios and for different positions of
the electrode.

\subsection{Samples }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{G3I20proc}
  \caption{ Photograph of sample $S_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate the center-line with a
    dashed line and eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the left side sealing o-ring.}
  \label{fig:SI3}
\end{figure}

@@

In Fig. \ref{fig:sem} we show some SEM images of the sample $S_3$,
including top views and lateral views taken after
the optical characterization was completed and the sample was cut
along its center-line (see Sec. \ref{sec:R}) from
three regions around the left side, the center, and the right side
of the sample shown in Fig. \ref{fig:SI3}.
\begin{figure}
  \centering
  \includegraphics[width=.3\textwidth]{sema}
  \includegraphics[width=.3\textwidth]{semb}
  \includegraphics[width=.3\textwidth]{semc}
  \includegraphics[width=.3\textwidth]{semd}
  \includegraphics[width=.3\textwidth]{seme}
  \includegraphics[width=.3\textwidth]{semf}
  \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
    micrographs of the sample $S_3$ taken from a region corresponding to the left
    side ((a) and (d)), center ((b) and (e)), and right side ((c) and
    (f)) along the center-line shown in Fig. \ref{fig:SI3}.}
  \label{fig:sem}
\end{figure}
We confirm that as we move away from the electrode, the pore
size and pore density diminish (panels (a) to (c) of
Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to
(f)). We remark that these micrographs were taken at three positions
that were not chosen to correspond to the eight locations at which we measured the
optical spectra. Thus, we didn't use SEM measurements for the quantitative
determination of neither the thickess nor the porosity; they were used
for the qualitative verification of the expected (Fig. \ref{fig:DE1})
and obtained (Table \ref{t:jpdv}) results. Actually, one of our
goals is to show that relatively inexpensive reflectance
measurements might be enough to characterize both the porosity and
etching rate variations along the sample.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R5migradvslambda}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $S_1$ ($I_1=5\,\text{mA}$). We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R10migradvslambda}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $S_2$ ($I_1=10\,\text{mA}$). We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{R20migradvslambda}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $S_3$ ($I_3=20\,\text{mA}$) (Fig. \ref{fig:SI3}),
    We show
    experimental results and results fitted through
    equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R20}
\end{figure}

@@

From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
the calculated density current $j_\perp$, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsjerr}
  \caption{Porosity vs. current density for the three samples
    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
    $p=mj_\perp+b$ with parameters
    $m=(0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}}$ and
    $b=0.551\pm.005$.
    }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit of the form $p=mj_\perp+b$ obtaining
\begin{equation}\label{eq:p}
  p\approx (0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}} j_\perp+(0.551\pm.005).
\end{equation}
Though the fit is reasonably good, it is noticeable that most of the data from
sample $S_2$ lie to the left of the fitted line while most of the data
from the other samples lie to the right. This discrepancies may be due
to the uncertainty in the positions $x_n$ (see Table \ref{t:xj}) due
to the ill defined distance from the edge of the sample (which roughly
corresponds to the position of the o-ring) to the edge of the cell. A
deformation of the o-ring when the cell is pressed against the wafer
would be equivalent to a rigid shift of the sample, i.e., to adding a
constant to all the positions $x_n$. Thus it is likely that the sign
and magnitude of that uncontrolled constant displacement changes among
samples.

Similarly, we can plot the fitted etching rate vs.
the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{vvsjerr}
  \caption{Etching rate vs. current density for three samples
    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
    $v=mj_\perp+b$ to the data with parameters $m=(0.312\pm
    0.017)(\text{cm}^2/\text{mA})(\text{nm/s})$ and
    $b=(0.44\pm0.09)\text{nm/s}$. }
  \label{fig:v}
\end{figure}
As for the porosity, excluding the points in the
immediate proximity of the wall of the cell, the remaining points
lie roughly on straight lines for each sample, and they
may all be approximated by a linear fit to all the data, from which we get
\begin{equation}\label{eq:v}
  v\approx (0.312\pm0.017)\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp +
  (0.44\pm0.09)\frac{\text{nm}}{{s}}.
\end{equation}
Similarly to
Fig. \ref{fig:p}, most data from sample $S_2$ lies to the left of the
fitted line and most of the data from $S_1$ and $S_3$  lie to the
right, which could be similarly explained and corrected.
These corrections are different for layers grown on different samples,
but for a multilayered system, produced by modulating the current $I$ in
time, a single correction ought to be enough for all the layers.

Using Eqs.  \eqref{Eq:ECMR}-\eqref{eq:v} we can calculate the
reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{jlrb}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $S_1$, $S_2$
    (shifted, see text) and  $S_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as discussed above and for visualization
purposes we applied small rigid translations to the samples along the
$x$ direction, thereby modifying $j_\perp$, before patching together
the reflectance spectra.
Notice that the experimental results may
be grouped along bright and dark bands that correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and their minima are not as low.

@@

\bibliographystyle{unsrt}
\bibliography{bibligrin}
\end{document}

>>>>

We assume that our electrolytic cell has the shape of a rectangular
prism (see Fig. \ref{f:celda}) with a horizontal base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is an
electrically grounded relatively good conductor. Within the electrolyte we position an electrode
which we assume is a thin conducting wire, insulated from the electrolyte
but for a small tip, which we approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig1.png}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid. The current flows through the electrolyte from the sample
    to the tip.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. In a
stationary situation
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, the potential
obeys Laplace's equation within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through, and the sign is consistent with the current direction in
Fig. \ref{f:celda}. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

  \includegraphics[width=\textwidth]{fig2}

@@

  \includegraphics[width=\textwidth]{fig3}

@@

The current density normal to the surface may now be obtained as
$j_\perp=-\sigma\partial\phi/\partial z$,
\begin{equation}
  \label{Eq:J}
  \begin{split}
    j_\perp(\bm r) =& \frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
      Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
    &\times \cosh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
  \end{split}
\end{equation}
Eq. \eqref{Eq:J} is a very rapidly convergent expression that allows,
in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
the substrate to produce the PS sample. As expected, the current
at the surface $z=0$ of the sample becomes more homogeneous as the
distance $z_0$ to the tip of the electrode and the height of the
electrolyte $c>z_0$ increase, as each term in the sum decays
approximately exponentially with increasing $z_0$.
Integrating over the surface of the sample we verify
\begin{equation}
  \label{eq:intj}
  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=I,
\end{equation}
as the contributions of opposite non-null reciprocal vectors cancel
out: as expected, all the charges that leave the sample find
their way  to the cathode across the electrolyte.

@@

\section{Procedures}
\label{sec:procedures}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{fig4a}\\[12pt]
  \includegraphics[width=.8\textwidth]{fig4b}\\[12pt]
  \includegraphics[width=.8\textwidth]{fig4c}

@@

\section{Results and Discussion}
\label{sec:discussion-results}
\subsection{Current Density}
\label{sec:current-density}
\begin{figure}
  \centering
  \begin{picture}(400,300)
    \put(0,0){\includegraphics[width=.8\textwidth]{fig5a.png}}
    \put(160,140){\includegraphics[trim=50 50 70 80,clip,width=.4\textwidth]{fig5b.png}}
  \end{picture}
  \caption{Normalized current density $j_\perp(x,y,0)/I$ for a system
    as in Figs. \ref{f:celda} and \ref{fig:DE1} for a cell of
    length $a = 2.01\,\text{cm}$ and width $b=1.48\,\text{cm}$, with
    the surface of the electrolyte at a height $c=1.0\,\text{cm}$, with a
    point-like electrode at $\bm r_0=(0.2\,\text{cm},
    0.74\,\text{cm},0.9\,\text{cm})$,  calculated through
    Eq. (\ref{Eq:J}) along the center line
    $y=0.74\,\text{cm}$. Inset: current over the whole surface.}
  \label{fig:DR1}
\end{figure}
In Fig. \ref{fig:DR1} we show the normalized current density $j_\perp(x,y,0)/I$ calculated through
Eq. \eqref{Eq:J} at the surface of the sample for our cell, as shown
in Figs. \ref{f:celda} and \ref{fig:DE1} and described in
Sect. \ref{sec:fabrication-ps-grin}). For these parameters we obtained
a large range of values for $ j_\perp/I\sim 0.11-.72\,\text{cm}^{-2}$
that vary mostly along the $x$ direction. Of course, this would differ
for cells with different aspect ratios and for different positions of
the electrode.

\subsection{Samples }
\label{sec:ps-grin-single}
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{fig6}
  \caption{ Photograph of sample $S_3$ prepared as described in
    Sec. \ref{sec:fabrication-ps-grin} using the same parameters as
    in Fig. \ref{fig:DR1} with a current $ I_3=20 \text{mA}$,
    during a time $t=250\text{s}$. We indicate the center-line with a
    dashed line and eight regions $x_i$
    $(i=1, 2,...8)$ centered at positions,
    $x'_1=0.2\text{cm}$,  $x'_2=0.4\text{cm}$, $x'_3=0.6\text{cm}$,
    $x'_4=0.8\text{cm}$, $x'_5=1\text{cm}$, $x'_6=1.2\text{cm}$,
    $x'_7=1.4\text{cm}$, $x'_8=1.6\text{cm}$, with $y_n=0.74\,\text{cm}$
    on which we measured reflectance spectra. Here,
    $x'_n=x_n+0.14\,\text{cm}$ is the position from the left side sealing o-ring.}
  \label{fig:SI3}
\end{figure}

@@

In Fig. \ref{fig:sem} we show some SEM images of the sample $S_3$,
including top views and lateral views taken after
the optical characterization was completed and the sample was cut
along its center-line (see Sec. \ref{sec:R}) from
three regions around the left side, the center, and the right side
of the sample shown in Fig. \ref{fig:SI3}.
\begin{figure}
  \centering
  \includegraphics[width=.3\textwidth]{fig7a}
  \includegraphics[width=.3\textwidth]{fig7b}
  \includegraphics[width=.3\textwidth]{fig7c}
  \includegraphics[width=.3\textwidth]{fig7d}
  \includegraphics[width=.3\textwidth]{fig7e}
  \includegraphics[width=.3\textwidth]{fig7f}
  \caption{Top ((a), (b), and (c)) and lateral ((d), (e), and (f)) SEM
    micrographs of the sample $S_3$ taken from a region corresponding to the left
    side ((a) and (d)), center ((b) and (e)), and right side ((c) and
    (f)) along the center-line shown in Fig. \ref{fig:SI3}.}
  \label{fig:sem}
\end{figure}
We confirm that as we move away from the electrode, the pore
size and pore density diminish (panels (a) to (c) of
Fig. \ref{fig:sem}) and the sample becomes much thinner (panels (d) to
(f)). We remark that these micrographs were taken at three positions
that were not chosen to correspond to the eight locations at which we measured the
optical spectra. Thus, we didn't use SEM measurements for the quantitative
determination of neither the thickness nor the porosity; they were used
for the qualitative verification of the expected (Fig. \ref{fig:DE1})
and obtained (Table \ref{t:jpdv}) results. Actually, one of our
goals is to show that relatively inexpensive reflectance
measurements might be enough to characterize both the porosity and
etching rate variations along the sample.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig8}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $S_1$ ($I_1=5\,\text{mA}$). We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R5}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig9}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $S_2$ ($I_1=10\,\text{mA}$). We show
  experimental results and results fitted through
  equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R10}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig10}
  \caption{Reflectance spectra at different positions
    ($x'_n=0.2-1.6\,\text{cm}$, $y=0.74\,\text{cm}$)
    on sample $S_3$ ($I_3=20\,\text{mA}$) (Fig. \ref{fig:SI3}),
    We show
    experimental results and results fitted through
    equations~\eqref{Eq:ECMR} and \eqref{Eq:Brugg}}.
  \label{fig:R20}
\end{figure}

@@

From the data in Table \ref{t:jpdv} we can plot the fitted porosity vs.
the calculated density current $j_\perp$, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig11}
  \caption{Porosity vs. current density for the three samples
    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
    $p=mj_\perp+b$ with parameters
    $m=(0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}}$ and
    $b=0.551\pm.005$.
    }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit of the form $p=mj_\perp+b$ obtaining
\begin{equation}\label{eq:p}
  p\approx (0.0122\pm0.001)\frac{\text{cm}^2}{\text{mA}} j_\perp+(0.551\pm.005).
\end{equation}
Though the fit is reasonably good, it is noticeable that most of the data from
sample $S_2$ lie to the left of the fitted line while most of the data
from the other samples lie to the right. This discrepancies may be due
to the uncertainty in the positions $x_n$ (see Table \ref{t:xj}) due
to the ill defined distance from the edge of the sample (which roughly
corresponds to the position of the o-ring) to the edge of the cell. A
deformation of the o-ring when the cell is pressed against the wafer
would be equivalent to a rigid shift of the sample, i.e., to adding a
constant to all the positions $x_n$. Thus it is likely that the sign
and magnitude of that uncontrolled constant displacement changes among
samples.

Similarly, we can plot the fitted etching rate vs.
the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig12}
  \caption{Etching rate vs. current density for three samples
    $S_1$, $S_2$, $S_3$. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$ (see text). We include a linear fit of the form
    $v=mj_\perp+b$ to the data with parameters $m=(0.312\pm
    0.017)(\text{cm}^2/\text{mA})(\text{nm/s})$ and
    $b=(0.44\pm0.09)\text{nm/s}$. }
  \label{fig:v}
\end{figure}
As for the porosity, excluding the points in the
immediate proximity of the wall of the cell, the remaining points
lie roughly on straight lines for each sample, and they
may all be approximated by a linear fit to all the data, from which we get
\begin{equation}\label{eq:v}
  v\approx (0.312\pm0.017)\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp +
  (0.44\pm0.09)\frac{\text{nm}}{{s}}.
\end{equation}
Similarly to
Fig. \ref{fig:p}, most data from sample $S_2$ lies to the left of the
fitted line and most of the data from $S_1$ and $S_3$  lie to the
right, which could be similarly explained and corrected.
These corrections are different for layers grown on different samples,
but for a multilayered system, produced by modulating the current $I$ in
time, a single correction ought to be enough for all the layers.

Using Eqs.  \eqref{Eq:ECMR}-\eqref{eq:v} we can calculate the
reflectance spectra for any
desired current density $j_\perp$ and etching time. This is
illustrated in Fig. \ref{fig:Rvsjl} for the parameters that correspond
to our samples.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{fig13}
  \caption{Reflection $R$ of a PS film as a function of the current density
    current $j_\perp$ and wavelength $\lambda$ for an etching time
    $t=250\,\text{s}$. Theory (left panel) and experiment (right
    panel, see text). We indicate with the numbers 1, 2, 3 the
    data corresponding to the corresponding samples $S_1$, $S_2$
    (shifted, see text) and  $S_3$.}
  \label{fig:Rvsjl}
\end{figure}
On the right hand side of the figure we display a quilt made by
patching together the experimental reflectance data corresponding to
Figs. \ref{fig:R5}- \ref{fig:R20}, ordered according to the
corresponding current density as presented in Table
\ref{t:jpdv}. Nevertheless, for the reasons mentioned above, we
eliminated the data corresponding to position $x'_1$ on all
samples. Furthermore, as discussed above and for visualization
purposes we applied small rigid translations to the samples along the
$x$ direction, thereby modifying $j_\perp$, before patching together
the reflectance spectra.
Notice that the experimental results may
be grouped along bright and dark bands that correspond closely to
those expected theoretically, though the experimental bands are somewhat shifted,
especially for low current densities, and their minima are not as low.

@@

\bibliographystyle{unsrt}
\bibliography{bibliography}
\end{document}
